\thesistitle

### 2019-07-30 sections/research.tex
Refactor literal variability

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/type2literal}
  \caption{Literal variability refactored.}
  \label{fig:type2literal}
\end{figure}

>>>>

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
// Original
public void printNice(String s){
	System.out.println("===");
	System.out.println(s);
	System.out.println("===");
}

public void printNice2(String s){
	System.out.println("---");
	System.out.println(s);
	System.out.println("---");
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// Refactored
public void printNice(String s){
	printNice(s, "===");
}

public void printNice2(String s){
	printNice(s, "---");
}

public void printNice(String s, String decoration){
	System.out.println(decoration);
	System.out.println(s);
	System.out.println(decoration);
}
\end{javacode}}
\end{parcolumns}
\caption{Literal variability refactored.}
\label{fig:type2literal}
\end{figure}
